General Physics Formula

### 2016-10-26 GRE Physics Prep/General Physics Formula.tex
Updates physics GRE prepare notes.

@@

@@

\textbf{String}
\begin{align}
    & v = \frac{\tau}{\mu} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Longitudinal Wave} (\textbf{pp.466 ch17 of \cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

@@

\paragraph{Conduction} (\textbf{pp.498 ch18 of \cite{book}})
\textbf{Thermal expansion}
\begin{align}
    & \Delta L = L \alpha \Delta T \\
    & \Delta V = V \beta \Delta T \\
    & \beta = 3 \alpha \\
    & Q = C \Delta T = cm \Delta T
\end{align}
\begin{defi}[Convection]
\nomenclature{Convection}{\nomrefpage.}
    Convection occurs when temperature differences cause an energy
    transfer by motion within a fluid
\end{defi}
\textbf{Radiation}
\begin{align}
    & P_\text{rad} = \sigma \varepsilon AT^4 \\
    & P_\text{abs} = \sigma \varepsilon AT_\text{evn}^4
\end{align}
\textbf{Conduction}
\begin{align}
    & P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L}  \\
    & P_\text{cond} = A \frac{T_H-T_C}{\sum(L_i/K_i)}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond}.png}
    \caption{pp.494 of \cite{book}}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond_series}.png}
    \caption{pp.495 of \cite{book}}
\end{figure}

@@

\begin{align}
    & \mathcal{E} = \frac{\diff W}{\diff q}
\end{align}
Cutting Magnetic field lines:
\begin{equation}
    \mathcal{E} = BLv 
\end{equation}
Cutting Magnetic field lines in circular motion:
\begin{equation}
    \mathcal{E} = B(\frac{1}{2}\omega R) R = \frac{1}{2}B\omega R^2
\end{equation}

\textbf{Circuit Rule}
\begin{itemize}
    \item \textbf{Loop Rule}. The algebraic sum of the changes in
        potential encountered in a complete traversal of any loop of a
        circuit must be zero.
    \item \textbf{Junction Rule}. The sum of the currents entering any
        junction must be equal to the sum of the currents leaving that
        junction
\end{itemize}

@@

\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})

@@

@@

\begin{align}
    & \lambda_n = \frac{\lambda}{n} \\
    & 2L = (m+\frac{1}{2})\frac{\lambda}{n_2} \text{ (thin film, max)}
    \\
    & d\sin{\theta} = m\lambda \text{ (Young's, max)}
\end{align}

@@

\section{Relativity}
\label{sec:Relativity}

\paragraph{Relativity} (\textbf{pp.1048 ch37 of \cite{book}})
\begin{align}
    \gamma &= \frac{1}{\sqrt{1-\beta^2}} \\
    \Delta t &= \gamma \Delta t_0 \\
    L &= L_0/\gamma \\
    x' &= \gamma(x-vt) \\
    t' &= \gamma(t-vx/c^2) \\
    u &= \frac{u'+v}{1+u'v/c^2} \\
    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}} \\
    f &= f_0 \sqrt{1-\beta^2} \\
    \vec{p} &= \gamma m \vec{v} \\
    E &= mc^2 + K = \gamma mc^2 \\
    E^2 &= (pc)^2 + (mc^2)^2
\end{align}

@@

\paragraph{Standard Model}
Read page 1244 of \cite{book}.
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{Standard-Model-of-Elementary-Particles}.pdf}
    \caption{Standard Model of Elementary Particles (from Wikipedia)}
\end{figure}

>>>>

\section{General}
\label{sec:Table}

\begin{table}[H]
    \centering
    \caption{Metric Prefix}
    \begin{tabular}{c c c}
        tera  & T     & $10^{12}$ \\
        giga  & G     & $10^{9}$ \\
        mega  & M     & $10^{6}$ \\
        kilo  & k     & $10^{3}$ \\
        centi & c     & $10^{-2}$ \\
        milli & m     & $10^{-3}$ \\
        micro & $\mu$ & $10^{-6}$ \\
        nano  & n     & $10^{-9}$ \\
        pico  & p     & $10^{-12}$ \\
    \end{tabular}
\end{table}

\paragraph{Rotation matrix}
Active rotation in the counter-clockwise $\theta$:
\begin{equation}
    \left(
    \begin{array}{cc}
        \cos{\theta} & -\sin{\theta} \\
        \sin{\theta} & \cos{\theta} \\
    \end{array}
    \right)
\end{equation}

@@

\begin{align}
L &= T- V\\
\frac{\diff}{\diff t} \left(\frac{\partial L}{\partial \dot{q}}\right)
    &= \frac{\partial L}{\partial q} \\
\dot{q} &= \frac{\partial H}{\partial p} \\
\dot{p} &= -\frac{\partial H}{\partial q}
\end{align}

@@

\textbf{String}
\begin{align}
    & v = \sqrt{\frac{\tau}{\mu}} \\
    & P_\text{avg} = \frac{1}{2}\mu v \omega^2 y_m^2
\end{align}
\textbf{Resonance}
\begin{align}
    n \lambda = 2L
\end{align}
\paragraph{Sound (Longitudinal) Wave} (\textbf{pp.466 ch17 of
\cite{book}})
\begin{align}
    & v = \sqrt{\frac{B}{\rho}} \\
    & s = s_m \cos(kx-\omega t) \\
    & \Delta p = \Delta p_m sin(kx-\omega r) \\
    & \Delta p_m = (v\rho \omega) s_m
\end{align}
\textbf{Sound Intensity}
\begin{align}
    & I = \frac{P}{A} \\
    & I = \frac{1}{2}\rho v \omega^2 s_m^2 \\
    & I = \frac{P_s}{4\pi r^2} \\
\end{align}
\textbf{Standing Wave Patterns in Pipes}
\begin{align}
    & f = \frac{v}{\lambda} = \frac{nv}{2L}\text{, $n=1,2,3,\cdots$} \\
    & f = \frac{v}{\lambda} = \frac{nv}{4L}\text{, $n=1,3,5,\cdots$}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch17.sound_wave}.png}
\end{figure}
\textbf{Beat}
\begin{align}
    f_\text{beat} = f_1 - f_2
\end{align}
\textbf{The Doppler Effect}
\begin{align}
    f' = f \frac{ v \pm v_D}{ v\pm v_s}
\end{align}
The signs are chosen such that $f'$ tends to be \textit{greater} for
motion toward and \textit{less} for motion away.
\textbf{Shock wave}
\begin{align}
    \sin{\theta} = \frac{v}{v_s}\text{ , $v_s\geq v$}
\end{align}

@@

\paragraph{Conduction} (\textbf{pp.498 ch18 of \cite{book}})
\textbf{Thermal expansion}
\begin{align}
    & \Delta L = L \alpha \Delta T \\
    & \Delta V = V \beta \Delta T \\
    & \beta = 3 \alpha \\
    & Q = C \Delta T = cm \Delta T
\end{align}
\begin{defi}[Convection]
\nomenclature{Convection}{\nomrefpage.}
    Convection occurs when temperature differences cause an energy
    transfer by motion within a fluid
\end{defi}
\textbf{Radiation}
\begin{align}
    & P_\text{rad} = \sigma \varepsilon AT^4 \\
    & P_\text{abs} = \sigma \varepsilon AT_\text{evn}^4
\end{align}

\textbf{Black Body Radiation}
Plank's law:
\begin{equation}
    I(\mu,T) = \frac{2h\mu^3}{c^2} \frac{1}{e^{\frac{h\mu}{kT}-1}}
\end{equation}
Wien's displacement law:

Wien's displacement law shows how the spectrum of black-body radiation
at any temperature is related to the spectrum at any other
temperature. If we know the shape of the spectrum at one temperature,
we can calculate the shape at any other temperature. Spectral
intensity can be expressed as a function of wavelength or of
frequency.

A consequence of Wien's displacement law is that the wavelength at
which the intensity per unit wavelength of the radiation produced by a
black body is at a maximum, $\lambda_\text{max}$, is a function only of the temperature:
\begin{equation}
    \lambda_\text{max}=\frac{b}{T}
\end{equation}
where the constant $b$, known as Wien's displacement constant.
\textbf{Conduction}
\begin{align}
    & P_\text{cond} \equiv \frac{Q}{t} = kA \frac{T_H-T_C}{L}  \\
    & P_\text{cond} = A \frac{T_H-T_C}{\sum(L_i/K_i)}
\end{align}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond}.png}
    \caption{pp.494 of \cite{book}}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{ch18.heat_cond_series}.png}
    \caption{pp.495 of \cite{book}}
\end{figure}

@@

\begin{align}
    & \mathcal{E} = \frac{\diff W}{\diff q}
\end{align}
Cutting Magnetic field lines:
\begin{equation}
    \mathcal{E} = BLv 
\end{equation}
Cutting Magnetic field lines in circular motion:
\begin{equation}
    \mathcal{E} = B(\frac{1}{2}\omega R) R = \frac{1}{2}B\omega R^2
\end{equation}
For electric generator:
\begin{equation}
    E_\text{max} = nBA_\text{rea}\omega
\end{equation}
\textbf{Circuit Rule}
\begin{itemize}
    \item \textbf{Loop Rule}. The algebraic sum of the changes in
        potential encountered in a complete traversal of any loop of a
        circuit must be zero.
    \item \textbf{Junction Rule}. The sum of the currents entering any
        junction must be equal to the sum of the currents leaving that
        junction
\end{itemize}

@@

\begin{align}
    & X_C = \frac{1}{\omega_d C} \\
    & X_L = \omega_d L \\
    & V = I X \\
    & Z_\text{impedance} = \text{vector sum of all above} \\
    & Z = \sqrt{R^2+(X_L-X_C)^2}  \text{ for simple RLC circuit}
\end{align}
% \begin{itemize}
%     \item \textbf{Resisitor} $V_R$ is in phase with $I$.
%     \item \textbf{Capacitor} $V_C$ lags $I$ by 90 degree.
%     \item \textbf{Inductor} $V_C$ preceeds $I$ by 90 degree.
% \end{itemize}
\paragraph{Maxwell's Equations} (\textbf{pp.869 of \cite{book}})

@@

\section{Optics}
\label{sec:Optics}

@@

\begin{align}
    & n = \frac{c}{v_\text{medium}} \\
    & \lambda_n = \frac{\lambda}{n} \\
    & 2L = (m+\frac{1}{2})\frac{\lambda}{n_2} \text{ (thin film, max)}
    \\
    & d\sin{\theta} = m\lambda \text{ (Young's, max)}
\end{align}

@@

\paragraph{Lenses}

\begin{align}
    & \frac{1}{s_o} + \frac{1}{s_i} = \frac{1}{f}
\end{align}
\begin{table}[H]
    \centering
    \begin{tabular}{c c c}
        Quantity & + & -\\
        \hline
        $s_i$ & real & virtual \\
        \hline
        $s_o$ & real & virtual \\
        \hline
        $f$ & convex & concave \\
        \hline
    \end{tabular}
\end{table}
\section{Relativity}
\label{sec:Relativity}

\paragraph{Relativity} (\textbf{pp.1048 ch37 of \cite{book}})
\begin{align}
    \gamma &= \frac{1}{\sqrt{1-\beta^2}} \\
    \Delta t &= \gamma \Delta t_0 \\
    L &= L_0/\gamma \\
    x' &= \gamma(x-vt) \\
    t' &= \gamma(t-vx/c^2) \\
    u &= \frac{u'+v}{1+u'v/c^2} \\
    f &= f_0 \sqrt{\frac{1-\beta}{1+\beta}}\text{ (away)} \\
    v &= \frac{|\Delta\lambda|}{\lambda_0}c\,( \text{ away, for } v<<c) \\
    f &= f_0 \sqrt{1-\beta^2} \text{ (perpendicular)}\\
    \vec{p} &= \gamma m \vec{v} \\
    E &= mc^2 + K = \gamma mc^2 \\
    E^2 &= (pc)^2 + (mc^2)^2
\end{align}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/Hydrogen_spectrum_series.pdf}
    \caption{Hydrogen spectrum series}
\end{figure}
\begin{table}[H]
    \centering
    \caption{Three common decay processes}
    \begin{tabular}{c c}
        Decay name & Process \\
        $\alpha$ & Emitting a Helium Nucleus (two protons and two
        neutrons) \\
        \hline
        $\beta$ & $n\to p+e^- \bar{v_e}$ or $p\to n+e^+ +v_e$ \\
        \hline
        $\gamma$ & Only photon (light ray) emitted \\
        \hline
    \end{tabular}
\end{table}

\section{Standard Model}
Read page 1244 of \cite{book}.
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\linewidth]{pics/{Standard-Model-of-Elementary-Particles}.pdf}
    \caption{Standard Model of Elementary Particles (from Wikipedia)}
\end{figure}
